---
title: "Network_visualization"
author: "Seo Wook Choi"
date: "2019-08-25"
output: html_document
---

## Network visualization (ego and contract)
This is based on the part of project during Micron data science intern (2019).
The original data was Skype call between employees. However, there is a security issue that I cannot present any of those information personally. The example is based on genertaed network and name data (all fake).

### Egonet
Most cases, presenting whole network in one plot makes reader cannot understand nothing from it.
When it comes to 100 vertices, whole netowrk plot seems to be meaningless.
In this case, engonet helps the visualzation to focuse on specific nodes of interest.
```{r, message=FALSE}
library(igraph)
library(tidyverse)
library(randomNames)
set.seed(4)
randomdata=randomNames(500,which.names="both",sample.with.replacement = FALSE,return.complete.data=TRUE)
g <- erdos.renyi.game(500, 5000, type = "gnm",directed=TRUE) %>%
  set_vertex_attr("ethnicity", value = randomdata$ethnicity)
row.names(randomdata)=paste(randomdata$first_name,randomdata$last_name,sep=", ") 
g.adjac=as_adjacency_matrix(g)
V(g)$name=rownames(randomdata)

set_vertex_attr(g,"ethnicity",value=randomdata$ethnicity)
selnodes <- V(g)[name %in% "Wyatt, Raetz"]
selnodes <- V(g)[name %in% "Laura, Vasquez-Romero"]
#selnodes <- V(wiki.graph)[name %in% "Roy, Abbagail"]
# get their network_c neighborhood 
selegoV <- ego(g, order=1, nodes = selnodes, mode = "all", mindist = 0)
selegoG <- induced_subgraph(g,unlist(selegoV))
layout <- layout.lgl(selegoG,repulserad=500)
plot.igraph(selegoG
            ,vertex.label=V(selegoG)$name
            ,layout=layout
            ,side=1
            ,edge.arrow.size=0.2
            ,vertex.label.font=1
            ,vertex.label.cex=1.2
            ,edge.width=0.5
            ,mark.border=NA
            ,vertex.label.dist=0.5  
            ,vertex.label.degree=-pi/2
            ,vertex.label.family="sans" #Helvetica"
)


```

### Contract
The "contract.vertices" function is to collapse the nodes with same traits.
In original example in Micron project, it was employees' postion name.
In this case, randomly assigned ethnicity in the same clique (connected subnetworks).


```{r }
index=as.integer(as.factor(randomdata$ethnicity))
index=replace_na(index,max(index,na.rm=TRUE)+1)
network_c<- contract.vertices(g,index, vertex.attr.comb="first")
network_c
V(network_c)$name=c("Latino", "White", "Asian", "Black", "Native","Other")
network_c2=igraph::simplify(network_c, remove.multiple = TRUE, remove.loops = TRUE)
plot.igraph(network_c2
            ,vertex.label=V(network_c2)$name
            ,layout=layout
            ,side=1
            ,edge.arrow.size=0.2
            ,vertex.label.font=1
            ,vertex.label.cex=1.2
            ,edge.width=0.5
            ,mark.border=NA
            ,vertex.label.dist=0.5  
            ,vertex.label.degree=-pi/2
            ,vertex.label.family="sans" #Helvetica"
)

```

### Adjust Size of nodes based on centrality (or hub and authority)
This part will be posted later.